---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mleb

<!-- badges: start -->
<!-- badges: end -->

The goal of mleb is to fit the modified likelihood Empirical Bayes (MLEB) estimator using the kernel Tweedie formula.
Parameters \code{(b, s)} can be explicitly supplied or automatically determined using 
Stein's Unbiased Risk Estimate (\code{"sure"}) or plug-in (\code{"plugin"}) methods.

## Installation

You can install the development version of mleb from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("wenkuangyu/mleb")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mleb)

# generate observations
set.seed(1037)
theta <- rep(c(0, 5), c(950, 50))
X <- theta + rnorm(1000)

fit <- mleb(X, method = 'plugin')

fit2 <- mleb(X, method = 'sure')

matplot(X, cbind(fit$mono_tweedie, fit2$mono_tweedie), ylab = '')

# average squared errors
c(mean((fit$mono_tweedie - theta)^2), mean((fit2$mono_tweedie - theta)^2))
```

